Halo alignments with large scale tidal and velocity fields

### 2013-03-13 paper/main.tex
more text on previous work

\citep{Libeskind2013} %various alignments
\citep{Libeskind2012} %varios alignments
\citep{Faltenbacher2009} %galaxy alignments with mocks
\citep{Paz2008} %angular momentum alignments
\citep{Platen2008} %alignment in voids
\citep{Lee2007}%Obs. spin alignment

\begin{itemize}
\item 
\citep{Codis2012}
Studies the alignment of the sping of dark matter halos realtive to
the surrounding large scale structure and to the tidal tensor
eigenvalues.

>>>>

\citep{Libeskind2013} %various alignments
\citep{Libeskind2012} %varios alignments

\citep{Faltenbacher2009} %galaxy alignments with mocks
\citep{Paz2008} %angular momentum alignments
\citep{Platen2008} %alignment in voids
\citep{Lee2007}%Obs. spin alignment

\begin{itemize}
\item
\citep{Zhang2009}
Study the spin and shape alignment against filaments.

They use a dark matter simulation with $1024^3$ DM particles in a
periodic box of $100$ \hMpc on a side. The particle mass is
$6.92\times10^{7}$\hMsun. Dark matter haloes are found using a FOF
algorithm with a linking length of 0.2 times the interparticle
distance. Only halos with more than 500 particles are retained for
further analysis.

The angular momentum is measured with positions repect to the center
of mass and the shape is determined using the non-normalized moment of
inertia tensor.

The environment is found using the hessian of the density. The density
field was interpolated over a $1024^3$ grid and then smoothed with a
Gaussian filter of scale $R_{s}2.1$\hMpc. There are two methods to
define the direction of a filament. The first method uses the
eigenvalues of the hessian density, howevere they define the filament
direction with the eigenvector corresponding the single positive
eigenvalue of the hessian. The second method used a line that
connects the two terminal halos in a filament segment.

The characterization of the alingment with the $\cos(\theta)$
statistic. For the method that uses the eigenvectors, they find that
the strenght of the spin alignment decreases with halo mass. For the
shape they study the alingment of the major axis with the
filament. The find an alignment signal in all mass bins, with an stronger
effect for more massive halos.

In a final experiment they measure the spin alignment in four
different samples that separated by the strength of the shape
alignment. They find that halos anticorrelated in shape, show a strong
sping correlation going to the extreme where there is a strong spin
anticorrelation for halos with a strong shape correlation. This means
that the halos with strong spin alignment are not the same halos
showing strong shape alignment.

\item 
\citep{Codis2012}
Studies the alignment of the spin of dark matter halos relative to
the surrounding large scale structure and to the tidal tensor
eigenvalues.
